Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-20 manuscript/manuscript.tex
Edit the adaptive discretization section

\noindent
\textit{Step 1}: Check that the tesseroid satisfies the following inequality for each
dimension $L_i$ of the tesseroid:

@@

\noindent
\textit{Step 2}: If none of the dimensions of the tesseroid fail inequality
\ref{eq:condition}, then compute the gravitational effect of the tesseroid using a
second-order GLQ (Eq. \ref{eq:glq-var-dens})

While keeping the GLQ fixed on second orders, the adaptive
discretization algorithm starts by checking that the following
inequality is satisfied:

\begin{equation}
    \frac{d}{L_i} \geq D,
\label{eq:distance-size-ratio}
\end{equation}

\noindent where $i \in \{\lambda, \phi, r\}$, $d$ is the distance
between the geometric centre of the tesseroid and the computation
point, and $D$ is a predefined value called distance-size ratio.
If the inequality \ref{eq:distance-size-ratio} is not held for at least
one spherical coordinate, then the tesseroid must be divided by half in
that direction.
On the contrary, if the inequality is satisfied for every spherical
coordinate, the algorithm computes the desired gravitational field using the
GLQ approximation.
A complete description of the modified adaptive discretization
algorithm can be found in \citet{Uieda2016}.

In summary, the distance-size ratio $D$ determines indirectly how many
times the tesseroids will be divided, and therefore efficiently
regulates both the accuracy of the algorithm and its computation time.
Moreover, it limits the computation time by stopping the division of
the tesseroids when their dimensions are lower than a certain value
(1mm), assuming that such small tesseroids do not modifies
significantly the desired gravitational field.

On the other hand, the value assigned to the distance-size ratio $D$
cannot be easily related to the error of the approximation, thus the
choice of the value of $D$ to get an acceptable accuracy must be
empirically determined beforehand.
In order to overcome this, \citet{Uieda2016} compared the numerical
computation with the analytical solution for a spherical shell with
homogeneous density.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{figures/spherical-shell.pdf}
\caption{
    Spherical shell with inner and outer radii $R_1$ and $R_2$, respectively.
    The computation point $Q$ is located on the $z$ axe at a distance $r$ from
    the centre of the shell.
    For our purposes we will assume that $Q$ is outside the outer radii,
    i.e. $r > R_2$.
    }
\label{fig:spherical-shell}
\end{figure}

@@

The equation \ref{eq:shell-pot} allows to easily obtain the exact
gravity potential generated by a spherical shell with a variable
density in depth on any outside point located on the $z$ axe.
Due to the rotational symmetry along any axe that passes through the
centre of the shell, the expression in equation \ref{eq:shell-pot}
reproduces the gravity potential field on any outside point at distance
$r$ from its centre.

@@

First, by solving the integral on equation \ref{eq:shell-pot}, we obtained the
gravitational potential generated by a spherical shell with this density on
any external point at distance $r$ from its centre:

>>>>

\textit{Step 1}: Check that the tesseroid satisfies the following inequality for each
dimension $L_i$ of the tesseroid:

@@

\textit{Step 2}:
If none of the dimensions of the tesseroid fail inequality
\ref{eq:condition}, then compute the gravitational effect of the tesseroid using a
second-order GLQ (Eq. \ref{eq:glq-var-dens}).
Add the computed effect to a running total.

\textit{Step 3}:
If any dimension fails inequality \ref{eq:condition}, split the tesseroid in half along
the offending dimensions.
Repeat steps 1-3 for all smaller tesseroids until none are left.

\textit{Final step}:
By the end of the algorithm, the running total will be the gravitational effect of the
tesseroid.

Notice that the distance-size ratio $D$ determines how many
times the tesseroids will be divided.
Therefore, it effectively regulates both the accuracy of the algorithm and its
computation time.
An optimal value for $D$ cannot be directly calculated from the desired accuracy level.
Instead, it is empirically determined by comparing the numerical results with the
analytical solution for a spherical shell.
\citet{Uieda2016} used a shell with homogeneous density to determine optimal values of
$D$.
Here, we will repeat the numerical experiment using analytical expressions for shells
with density varying according to exponential and linear functions of $r$.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{figures/spherical-shell.pdf}
\caption{
    Spherical shell with inner and outer radii $R_1$ and $R_2$, respectively.
    The computation point $Q$ is located on the $z$ axe at a distance $r$ from
    the center of the shell.
    For our purposes we will assume that $Q$ is outside the outer radii,
    i.e. $r > R_2$.
    }
\label{fig:spherical-shell}
\end{figure}

@@

The equation \ref{eq:shell-pot} allows to easily obtain the exact
gravity potential generated by a spherical shell with a variable
density in depth on any outside point located on the $z$ axe.
Due to the rotational symmetry along any axe that passes through the
center of the shell, the expression in equation \ref{eq:shell-pot}
reproduces the gravity potential field on any outside point at distance
$r$ from its center.

@@

First, by solving the integral on equation \ref{eq:shell-pot}, we obtained the
gravitational potential generated by a spherical shell with this density on
any external point at distance $r$ from its center:
